Analysis of Odd one out experiment

### 2019-07-09 reports/odd_one_out/analysis_oddoneout.Rmd
minor changes in plots

p <- df_onecat_distances %>% 
  ggplot(aes(x = distance)) + 
  geom_histogram(bins = 30) + 
  theme(aspect.ratio = 1) +
  geom_segment(data = df_segments, aes(x=x,xend=xend,y=y,yend=yend)) +
  annotate(x = qs[3:5]-c(3,1,-0.6), y = c(19,19,19), label = c("2.","3.","4."), geom = "label", size = 5) +
  ggtitle(sprintf("Category: %s",this_cat)) +
  xlab("Distance") +
  ylab("Count")
p  
ggsave(file.path(plots_dir, "Fig_chp3_distance_histogram.svg"), p, width = 6, height = 6)

@@

p0 <- df %>% ggplot(aes(x = d_ratio, y =correct))+
    geom_point(alpha=0.5)

predframe <- tibble(d_ratio= df$d_ratio)

predframe$correct <- predict(glm2,newdata=predframe,type="response",re.form=NA)
p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Distance ratio") + 
  ylab("Perc. correct") +
  theme(text = element_text(size = 24))

@@

p <- metrics %>% 
  filter(metric!= "ssim_correct") %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_discrete(labels = c("Humans", "GIST", "HOG", "RGB", "SIFT")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict human peformance")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman.svg"), p, width = 6, height = 6)

>>>>

p <- df_onecat_distances %>% 
  ggplot(aes(x = distance)) + 
  geom_histogram(bins = 30) + 
  theme(aspect.ratio = 0.5) +
  geom_segment(data = df_segments, aes(x=x,xend=xend,y=y,yend=yend)) +
  annotate(x = qs[3:5]-c(3,1,-0.6), y = c(19,19,19), label = c("2.","3.","4."), geom = "label", size = 5) +
  ggtitle(sprintf("Category: %s",this_cat)) +
  xlab("Distance") +
  ylab("Count")
p  
ggsave(file.path(plots_dir, "Fig_chp3_distance_histogram.svg"), p, width = 9, height = 6)

@@

p0 <- df %>% ggplot(aes(x = d_ratio, y =correct))+
    geom_point(alpha=0.5, position = position_jitter(height = 0.03))

predframe <- tibble(d_ratio = df$d_ratio)

predframe$correct <- predict(glm2,newdata=predframe,type="response",re.form=NA)

p <- p0 + geom_point(data=predframe,colour="red")+
  geom_line(data=predframe,colour="red",aes(group=1)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  xlab("Distance ratio") + 
  ylab("Perc. correct") +
  theme(text = element_text(size = 24))

@@

p <- metrics %>% 
  filter(metric!= "ssim_correct", metric!= "correct") %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_discrete(labels = c("GIST", "HOG", "RGB", "SIFT")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict human performance")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman.svg"), p, width = 6, height = 6)
